### 2023-04-03 reachable-resilience.tex
up

\begin{proof}
By Proposition~\ref{post*}, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
Let us now show that the downward-reachability problem is decidable for Petri nets.
Let us consider a downward closed set $D$ in a Petri net.
$D$ is  defined by ... states where your number of counter is bounded by a constant, and others where it is unbounded. You have $m$ counters where it is bounded by $n$
then you have $m \times n$ possibilities for the values in these counters
you have unlimited possibilities for the values of the other counters,
but that is where the submarking problem comes in handy,
i.e. you ask the submarking problem for all of the $m \times n$ possibilities.

@@

\begin{theorem}
The resilience problem is undecidable for effective WSTS with  strong  compatibility 
when
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{theorem}

>>>>

\begin{proof}
By Proposition~\ref{post*}, a basis of $\uparrow \post^*(s)$ is computable for every state $s$ iff the downward-reachability problem is decidable.
Let us now show that the downward-reachability problem is decidable for Petri nets.
Let us consider a downward closed set $D$ in a Petri net.
Let us consider $B$ a basis of the upward closed set $S \setminus D$.

$D$ is  defined by ... states where your number of counter is bounded by a constant (deduce this from ... having to be smaller than elements of the basis $B$), and others where it is unbounded. You have $m$ counters where it is bounded by $n$
then you have $m \times n$ possibilities for the values in these counters
you have unlimited possibilities for the values of the other counters,
but that is where the submarking problem comes in handy,
i.e. you ask the submarking problem for all of the $m \times n$ possibilities.

@@

\begin{theorem}
The state resilience problem is undecidable for effective WSTS with  strong  compatibility 
when
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{theorem}
